%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{engineer_cv} % a4paper for A4

% Command for printing skill overview bubbles
\newcommand\skills
{
	\smartdiagram[bubble diagram]
	{
		\textbf{~~~~Ruining economies~~~~~},
		\textbf{~Modelling~},
		\textbf{Economics},
		\textbf{Matlab models},
		\textbf{~R~},
		\textbf{~~~Statistics~~~}
	}
}

% Projects text
\projects
{
	\textbf{HSM} - A hierarchical state machine in C without the use of dynamical allocation.\\
	\textbf{sString} - A C string module that does not use dynamical allocation.\\
	\textbf{Real Engine} - Developed a custom Game Engine in C++ with the following libraries: \\
	Irrlicht SDK, Havok Physics and Animation SDK, LUA scripting language and Irrklang SDK.
}

%My custom made command.
\newcommand{\titleOnoma}[2]
{
	\textbf{#1:} #2\\
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

\cvname{Maria Kaneli} % Your name
\cvjobtitle{Statistical Data Analyst} % Job
\cvlinkedin{/in/mariakaneli}
\cvgithub{mkanel}
\cvnumberphone{(+30) 697 81 77 863} % Phone number
\cvsite{tedicreations.github.io} % Personal website
\cvmail{m.kaneli@yahoo.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

	\makeprofile % Print the sidebar

	%----------------------------------------------------------------------------------------
	%	 SUMMARY
	%----------------------------------------------------------------------------------------

	\section{Summary}

        I am able to manage economical/mathematical models and to do data analysis. You should write something about yourself. See what I wrote.

	My main interest is embedded and mechatronic systems. I love how algorithms control machines at will. Creativity is something that comes easy with me and most of it is expressed through out my art. Innovation is something hard to achieve and I try my best to examine the new Internet of Things field for new opportunities.

	%----------------------------------------------------------------------------------------
	%	 EDUCATION
	%----------------------------------------------------------------------------------------

	\section{Education and training}

	\begin{longList} % Environment for a list with descriptions
		\longListItem
			{2015 - 2018}
			{}
			{MSc., Banking and Finace \textnormal{(GPA: 7.77/10)}}
			{\\\href{https://www.econ.uth.gr/}{The Department of Economics on Applied Economics, Univercity of Thessaly, Volos Greece}\\{{\bf Thesis:} Dynamic Study of a nonlinear Keynesian model in the market of a Good. 8.3/10}}
			{}
			{}
			\\
		\longListItem
			{2010 - 2015}
			{}
			{BSc., Statistics and Actuarial - Financial Mathematics \textnormal{(GPA: 7.02/10)}}
			{\\\href{https://www.math.aegean.gr/}{The Department of Mathematics, Univercity of Aegean, Samos Greece}\\{{\bf Thesis:} ????????????}}
			{}
			{}
			\\
		\longListItem
			{2018}
			{}
			{Certification of Diana Award Anti-Bulling Ambassador}
			{Athens}
			{}
			{}
		\longListItem
			{2017}
			{}
			{24ο Summer School/Conference Dynamical Systems and Complexity}
			{Volos}
			{}
			{}
		\longListItem
			{2016}
			{}
			{Scientific presentation about “Democracy and Economy”}
			{Volos}
			{}
			{}
		\longListItem
			{2015}
			{}
			{Scientific presentation about “Revaluated of the implications on the European structural funds to Greece}
			{Volos}
			{}
			{}
		\longListItem
			{2015}
			{}
			{4ο Panhellenic Conference on Applied Economics}
			{Volos}
			{}
			{}
	\end{longList}


	%----------------------------------------------------------------------------------------
	%	 PROFESSIONAL EXPERIENCE PAGE 1
	%----------------------------------------------------------------------------------------

	\section{Professional Experience}

	\begin{longList} % Environment for a list with descriptions
		\longListItem
			{01/07/2015}
			{28/08/2015}
			{Assistant accountant}
			{Fotiou Dimitrios Accounting Department}
			{}
			{\begin{itemize}
				\item Organize and maintain financial records.
				\item Compute taxes owed, prepare tax returns and ensure prompt payment.
                                \item Inspect account books and accounting systems to keep up to date.
                                \item Provide auditing services for businesses and individuals.
			\end{itemize}}
			\\
        \end{longList}


        \clearpage

	\infographics

	%----------------------------------------------------------------------------------------
	%	 THEORETICAL KNOWLEDGE
	%----------------------------------------------------------------------------------------

	\section{Theoretical Knowledge}

	\begin{longList} % Environment for a list with descriptions
		\longListItem
			{}
			{}
			{Classical and modern Control Theory of dynamical systems}
			{}
			{}
			{\begin{itemize}
				\item Classical and modern Control Theory of dynamical systems.
				\item Stability, Controllability and observability.
				\item Adaptive, Hierarchical, Intelligent, Optimal, Robust and Stochastic control.
				\item System identification.
				\item Neural network and fuzzy logic control.
			\end{itemize}}
			\\
		\longListItem
			{}
			{}
			{Robotics}
			{}
			{}
			{\begin{itemize}
				\item (Inverse) Kinematics and dynamics theory of movement.
			\end{itemize}}
			\\
		\longListItem
			{}
			{}
			{Mechatronics}
			{}
			{}
			{\begin{itemize}
				\item Electronics.
				\item Sensor data acquisition and actuator control.
			\end{itemize}}
			\\
		\longListItem
			{}
			{}
			{Telematics}
			{}
			{}
			{\begin{itemize}
				\item SCADA systems.
				\item M2M interface.
			\end{itemize}}
			\\
		\longListItem
			{}
			{}
			{Telecommunications}
			{}
			{}
			{\begin{itemize}
				\item Laplace, Z- transform.
			\end{itemize}}
			\\
	\end{longList}

	%----------------------------------------------------------------------------------------
	%	 SPARE TIME ACTIVITIES ( HOBBIES )
	%----------------------------------------------------------------------------------------

	\section{Spare time activities}

	\begin{longList} % Environment for a list with descriptions
		\longListItem
			{}
			{}
			{}
			{\begin{itemize}
			  \item Traditional dance, ballet and hip-hop.
                          \item Voluntary participant in the Environmental Team.
			\end{itemize}}
			{}
			{}
			\\
	\end{longList}

	\raggedleft{\today}

\end{document}
